Enhancing Underwater Imagery using Generative Adversarial Networks

### 2017-09-28 files/paper/PlainPaper.tex
plain version added
update

\documentclass[letterpaper, 10pt, conference]{ieeeconf}

@@

\IEEEoverridecommandlockouts
\overrideIEEEmargins

@@

\title{Enhancing Underwater Imagery using Generative Adversarial Networks}
\author{Cameron Fabbri$^{1}$, Md Jahidul Islam$^{2}$, and Junaed Sattar$^{3}$
\thanks{				
  The authors are with the Department of Computer Science and Engineering, University of Minnesota-Twin  Cities, MN 55455, USA. \newline
 {\tt\small\{$^{1}$fabbr013, $^{2}$islam034, $^{3}$junaed\}@umn.edu}
}
}

% \author{\IEEEauthorblockN{Cameron Fabbri$^{1}$}
% \IEEEauthorblockA{Information Directorate\\
% Air Force Research Laboratory \\
% Rome, NY, USA.\\
% cameron.fabbri@us.af.mil}
% \and
% \IEEEauthorblockN{Md Jahidul Islam \& Junaed Sattar}
% \IEEEauthorblockA{Department of Computer Science and Engineering\\University of Minnesota- Twin Cities, MN, USA.\\
% \{islam034, junaed\}@umn.edu }
% \and
% \IEEEauthorblockN{Junaed Sattar}
% \IEEEauthorblockA{Department of Computer Science and Engineering\\University of Minnesota- Twin Cities,MN, USA.\\
% junaed@umn.edu
%}

@@

\input{tex/abstract}
\input{tex/introduction}
\input{tex/related}
\input{tex/methodology.tex}
\input{tex/experiments}
\input{tex/conclusions}

\bibliography{cambibs}
\bibliographystyle{ieeetr}

>>>>

\documentclass[11pt, twocolumn]{article}

@@

@@

\title{Enhancing Underwater Imagery using Generative Adversarial Networks}
\author{Cameron Fabbri$^{1}$, Md Jahidul Islam$^{2}$, and Junaed Sattar$^{3}$
\thanks{				
  The authors are with the Department of Computer Science and Engineering, University of Minnesota-Twin  Cities, MN 55455, USA,
  and the $^{1}$Air Force Research Laboratory, Rome, NY \newline
 {\tt\small\{$^{1}$fabbr013, $^{2}$islam034, $^{3}$junaed\}@umn.edu}
 {\tt\small$^{1}$cameron.fabbri@us.af.mil}
}
}

@@

\input{tex/abstract}
\input{tex_plain_version/introduction}
\input{tex/related}
\input{tex_plain_version/methodology.tex}
\input{tex_plain_version/experiments}
\input{tex/conclusions}

\bibliography{cambibs}
\bibliographystyle{plain}
